---
title: " "
output:
  flexdashboard::flex_dashboard:
    logo: GNR_logo.png
    orientation: rows
    vertical_layout: scroll
    theme:
      version: 4
      bg: "#FFFFFF"
      fg: "#13293d"
      primary: "#FFFFFF"
    includes:
      in_header: OGheader.html
runtime: shiny
---


```{r setup, include=FALSE, echo=FALSE, warning =FALSE}

knitr::clean_cache(clean = TRUE)
knitr::opts_chunk$set(echo = FALSE)
# opts_chunk$set(comment="")
# 1. Load packages first, then source theme and functions
library(here)
source(here("R","packages.R"))
source(here("R","brand_theme.R"))
source(here::here("R", "functions.R"))
source(here("R", "plot_accessibility.R"))




## LOAD DEIDENTIFIED DATA FOR DISTRICT-LEVEL ANALYSIS
# Load the de-identified datasets for generating charts
vax_deidentified_cleaned <- read_csv(here("data", "clean", "vax_deidentified_cleaned.csv"), show_col_types = FALSE)
enteric_deidentified_cleaned <- read_csv(here("data", "clean", "enteric_deidentified_cleaned.csv"), show_col_types = FALSE)
VBD_deidentified_cleaned <- read_csv(here("data", "clean", "VBD_deidentified_cleaned.csv"), show_col_types = FALSE)

## DISTRICT PLOTS
# pre-generated District plots by program
vpds_district_plot <- readRDS(here::here("output", "vpds_district_plot.rds"))
vbds_district_plot <- readRDS(here::here("output", "vbds_district_plot.rds"))
enteric_district_plot <- readRDS(here::here("output", "enterics_district_plot.rds"))

# pre-generated District age pyramids
vpds_district_pyramid <- readRDS(here("output", "age_pyramids", "vpds_district_pyramid.rds"))
enterics_district_pyramid <- readRDS(here("output", "age_pyramids", "enterics_district_pyramid.rds"))
vbds_district_pyramid <- readRDS(here("output", "age_pyramids", "vbds_district_pyramid.rds"))

# Generate District horizontal bar charts for race distribution (ascending order)
vpds_dis_rac_bar <- generate_horizontal_bar_chart(
  data = vax_deidentified_cleaned,
  group_col_name = "race",
  disease_program = "Vaccine Preventable",
  county_name = "District"
)

enterics_dis_rac_bar <- generate_horizontal_bar_chart(
  data = enteric_deidentified_cleaned,
  group_col_name = "race",
  disease_program = "Enteric",
  county_name = "District"
)

vbds_dis_rac_bar <- generate_horizontal_bar_chart(
  data = VBD_deidentified_cleaned,
  group_col_name = "race",
  disease_program = "Vectorborne",
  county_name = "District"
)

# pre-generated District ethnicity pies
vpds_dis_eth_pie <- readRDS(here("output", "vpd_district_ethnicity_pie.rds"))
enterics_dis_eth_pie <- readRDS(here("output", "ent_district_ethnicity_pie.rds"))
vbds_dis_eth_pie <- readRDS(here("output", "vbd_district_ethnicity_pie.rds"))


## COUNTY PLOTS
# These files will be loaded by the R Markdown dashboard later.
Gvbd_gender <- readRDS(here("output", "Gvbd_gen_pie.rds"))
Gvbd_race <- readRDS(here("output", "Gvbd_rac_pie.rds"))
Gvbd_ethnicity <- readRDS(here("output", "Gvbd_eth_pie.rds"))

Gvpd_gender <- readRDS(here("output", "Gvpd_gen_pie.rds"))
Gvpd_race <- readRDS(here("output", "Gvpd_rac_pie.rds"))
Gvpd_ethnicity <- readRDS(here("output", "Gvpd_eth_pie.rds"))

Gent_gender <- readRDS(here("output", "Gent_gen_pie.rds"))
Gent_race <- readRDS(here("output", "Gent_rac_pie.rds"))
Gent_ethnicity <- readRDS(here("output", "Gent_eth_pie.rds"))

Nvbd_gender <- readRDS(here("output", "Nvbd_gen_pie.rds"))
Nvbd_race <- readRDS(here("output", "Nvbd_rac_pie.rds"))
Nvbd_ethnicity <- readRDS(here("output", "Nvbd_eth_pie.rds"))

Nvpd_gender <- readRDS(here("output", "Nvpd_gen_pie.rds"))
Nvpd_race <- readRDS(here("output", "Nvpd_rac_pie.rds"))
Nvpd_ethnicity <- readRDS(here("output", "Nvpd_eth_pie.rds"))

Nent_gender <- readRDS(here("output", "Nent_gen_pie.rds"))
Nent_race <- readRDS(here("output", "Nent_rac_pie.rds"))
Nent_ethnicity <- readRDS(here("output", "Nent_eth_pie.rds"))


Rvbd_gender <- readRDS(here("output", "Rvbd_gen_pie.rds"))
Rvbd_race <- readRDS(here("output", "Rvbd_rac_pie.rds"))
Rvbd_ethnicity <- readRDS(here("output", "Rvbd_eth_pie.rds"))

Rvpd_gender <- readRDS(here("output", "Rvpd_gen_pie.rds"))
Rvpd_race <- readRDS(here("output", "Rvpd_rac_pie.rds"))
Rvpd_ethnicity <- readRDS(here("output", "Rvpd_eth_pie.rds"))

Rent_gender <- readRDS(here("output", "Rent_gen_pie.rds"))
Rent_race <- readRDS(here("output", "Rent_rac_pie.rds"))
Rent_ethnicity <- readRDS(here("output", "Rent_eth_pie.rds"))


# Hepatitis Data (files not yet generated — uncomment once output RDS files exist)
# district_hep_object <- readRDS(here("output", "district_hep_time.rds"))
# Gwinnett_hep_object <- readRDS(here("output", "Gwinnett_hep_time.rds"))
# Newton_hep_object <- readRDS(here("output", "Newton_hep_time.rds"))
# Rockdale_hep_object <- readRDS(here("output", "Rockdale_hep_time.rds"))


# --- Define counties and programs ---
county_name <- c("Gwinnett", "Newton", "Rockdale")
program_name <- c("Vaccine Preventable", "Vectorborne", "Enteric")

VPD_program_name <- program_name[1] # "Vaccine Preventable"
VBD_program_name <- program_name[2] # "Vectorborne"
ENTERIC_program_name <- program_name[3] # "Enteric"



# 2. Keep only the "Global" objects you need for things like narratives
# Narrative file mapping
narrative_files <- list(
  "Vaccine Preventable" = "VPDs.Rmd",
  "Vectorborne" = "VBDs.Rmd",
  "Enteric" = "Enterics.Rmd",
  "Hep_C" = "Hepatitis_C.rmd",
  "about_lines" = "about_dashboard.rmd")


# Load all plots
all_plots <- readRDS(here::here("output", "plots", "all_dashboard_plots.rds"))
all_hep_plots <- readRDS(here::here("output", "plots", "all_hep_plots.rds"))
Gplot_list <- readRDS(here("output", "plots", "gwinnett_linebar_plots.rds"))

# 3. Define shorthand tags
tags <- htmltools::tags
div <- htmltools::div
```

<!-- # For skip link #main ID -->
<div id="main" tabindex="-1" style="outline: none;"></div>

<!-- Logo, contrast toggle, and Last Updated are injected into the navbar via OGheader.html JavaScript -->

# Vaccine-Preventable Illnesses {data-navmenu="District Overview"}

<h1>Gwinnett, Newton and Rockdale Vaccine Preventable Illnesses</h1>

```{r VPDs_summary, warning=FALSE, results='asis'}

# Read the pre-generated text summary
vpds_district_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator, cat() is used because it prints text directly, honoring the Markdown formatting.
 cat(vpds_district_lines, sep = "\n")
 cat(" ")

```



```{r 04_VPDs_district_plot, results='asis'}

# Create a container with VPD case rates plot and age pyramid side by side
div(
  class = "demographic-container",
  div(
    class = "demographic-charts",
    # VPD Case Rates Plot (60% width)
    div(
      class = "dashboard-card",
      style = "flex: 0 0 calc(60% - 10px) !important; min-width: 400px;",
      vpds_district_plot$plot,
      tags$span(class = "sr-only", vpds_district_plot$sr_text)
    ),
    # Age Pyramid (35% width)
    div(
      class = "dashboard-card age-pyramid-card",
      style = "flex: 0 0 calc(35% - 10px) !important; min-width: 280px;",
      vpds_district_pyramid$plot,
      tags$span(class = "sr-only", vpds_district_pyramid$sr_text)
    )
  )
)

cat(" ")

```

```{r results='asis'}

cat("<br>")

```

## {.no-title .no-box}

### {.no-title .no-box}

```{r demographic_dist_vpd, results='asis'}

# Create a container with demographic charts (race bar + ethnicity pie)
div(
  class = "demographic-container",
  h3("Demographic Distribution for Vaccine Preventable Illnesses", style = "width: 100%; margin-bottom: 20px;"),
  div(
    class = "demographic-charts",
    # Race Horizontal Bar Chart (55% width - ascending order)
    div(
      class = "dashboard-card race-bar-card",
      style = "flex: 0 0 calc(55% - 10px) !important; min-width: 300px;",
      vpds_dis_rac_bar$plot,
      tags$span(class = "sr-only", vpds_dis_rac_bar$sr_text)
    ),
    # Ethnicity Pie Chart (40% width)
    div(
      class = "dashboard-card ethnicity-pie-card",
      style = "flex: 0 0 calc(40% - 10px) !important; min-width: 250px;",
      vpds_dis_eth_pie$plot,
      tags$span(class = "sr-only", vpds_dis_eth_pie$sr_text)
    )
  )
)

```


## 

```{r, results='asis'}

cat("<br>")

```


## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Hepatitis Illnesses across the District</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r Hepatitis_C, warning=FALSE, results='asis'}

# Read the pre-generated  text summary
hepc_district_lines <- readLines(here("narratives", "Hepatitis_C.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(hepc_district_lines, sep = "\n")

cat(" ")

```



```{r hep_plot, results='asis'}

div(
  class = "dashboard-card",
  all_hep_plots$district$plot,
  tags$span(class = "sr-only", all_hep_plots$district$sr_text)
)

```





# Enteric Illnesses {data-navmenu="District Overview"}

<h1>Gwinnett, Newton and Rockdale Vaccine Enteric Illnesses</h1>

```{r 04_Enterics_Summary, results='asis'}
# Read the pre-generated accessible text summary
enterics_district_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_district_lines, sep = "\n")


cat(" ")
```



```{r 04_Enterics_district_plot, warning=FALSE, results='asis'}

# Create a container with Enteric case rates plot and age pyramid side by side
div(
  class = "demographic-container",
  div(
    class = "demographic-charts",
    # Enteric Case Rates Plot (60% width)
    div(
      class = "dashboard-card",
      style = "flex: 0 0 calc(60% - 10px) !important; min-width: 400px;",
      enteric_district_plot$plot,
      tags$span(class = "sr-only", enteric_district_plot$sr_text)
    ),
    # Age Pyramid (35% width)
    div(
      class = "dashboard-card age-pyramid-card",
      style = "flex: 0 0 calc(35% - 10px) !important; min-width: 280px;",
      enterics_district_pyramid$plot,
      tags$span(class = "sr-only", enterics_district_pyramid$sr_text)
    )
  )
)
cat("<br>")

```





## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic's Distribution for Enteric Illnesses</h3>
<<<<<<< HEAD
=======

## {.no-title .no-box}
>>>>>>> parent of 2c8217d (Merge pull request #1 from GNREPI/covid-report)

### {.no-title .no-box}

```{r demographic_dist_enteric, results='asis'}

# Create a container with demographic charts (race bar + ethnicity pie)
div(
  class = "demographic-container",
  h3("Demographic Distribution for Enteric Illnesses", style = "width: 100%; margin-bottom: 20px;"),
  div(
    class = "demographic-charts",
    # Race Horizontal Bar Chart (55% width - ascending order)
    div(
      class = "dashboard-card race-bar-card",
      style = "flex: 0 0 calc(55% - 10px) !important; min-width: 300px;",
      enterics_dis_rac_bar$plot,
      tags$span(class = "sr-only", enterics_dis_rac_bar$sr_text)
    ),
    # Ethnicity Pie Chart (40% width)
    div(
      class = "dashboard-card ethnicity-pie-card",
      style = "flex: 0 0 calc(40% - 10px) !important; min-width: 250px;",
      enterics_dis_eth_pie$plot,
      tags$span(class = "sr-only", enterics_dis_eth_pie$sr_text)
    )
  )
)

```





# Vectorborne Illnesses {data-navmenu="District Overview"}

<h1>Gwinnett, Newton and Rockdale Vectorborne Illnesses</h1>

```{r 04_VBD_text, warning=FALSE, results='asis'}

# Read the pre-generated accessible text summary
vbds_district_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_district_lines, sep = "\n")


cat(" ")

```


```{r 04_VBDs_district_plot, warning=FALSE, results='asis'}

# Create a container with VBD case rates plot and age pyramid side by side
div(
  class = "demographic-container",
  div(
    class = "demographic-charts",
    # VBD Case Rates Plot (60% width)
    div(
      class = "dashboard-card",
      style = "flex: 0 0 calc(60% - 10px) !important; min-width: 400px;",
      vbds_district_plot$plot,
      tags$span(class = "sr-only", vbds_district_plot$sr_text)
    ),
    # Age Pyramid (35% width)
    div(
      class = "dashboard-card age-pyramid-card",
      style = "flex: 0 0 calc(35% - 10px) !important; min-width: 280px;",
      vbds_district_pyramid$plot,
      tags$span(class = "sr-only", vbds_district_pyramid$sr_text)
    )
  )
)
cat(" ")

```





## {.no-title .no-box}

### {.no-title .no-box}

```{r demographic_dist_vbd, results='asis'}

# Create a container with demographic charts (race bar + ethnicity pie)
div(
  class = "demographic-container",
  h3("Demographic Distribution for Vectorborne Illnesses", style = "width: 100%; margin-bottom: 20px;"),
  div(
    class = "demographic-charts",
    # Race Horizontal Bar Chart (55% width - ascending order)
    div(
      class = "dashboard-card race-bar-card",
      style = "flex: 0 0 calc(55% - 10px) !important; min-width: 300px;",
      vbds_dis_rac_bar$plot,
      tags$span(class = "sr-only", vbds_dis_rac_bar$sr_text)
    ),
    # Ethnicity Pie Chart (40% width)
    div(
      class = "dashboard-card ethnicity-pie-card",
      style = "flex: 0 0 calc(40% - 10px) !important; min-width: 250px;",
      vbds_dis_eth_pie$plot,
      tags$span(class = "sr-only", vbds_dis_eth_pie$sr_text)
    )
  )
)

```





# **Gwinnett County**

<h1>Gwinnett County Community Health Data</h1>


```{r Gpop_callout, echo=FALSE}


Gpop <- "1,003,869" # Example R calculation
# The 'value' attribute automatically handles the large formatting.


valueBox(
  value = Gpop,
  icon = "fa-pencil",
  color = "primary"
)
cat(" ")


```




## 

### 

<h3 style="font-weight=bold; margin:0;">Vaccine Preventable Illnesses</h3>


```{r 04_GVPDs_text, results='asis'}

vpds_gwinnett_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vpds_gwinnett_lines, sep = "\n")

cat(" ")

cat("<br>")

```


##

```{r GVPD_bar, results='asis'}

vplot_obj <- Gplot_list$bar_chart$`Vaccine Preventable`$plot

vplot_obj


```

###

```{r GVPD_timeplot, results='asis'}


Gvplot_list_obj <- Gplot_list$line_charts$`Vaccine Preventable`$plot

Gvplot_list_obj


```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vaccine Preventable Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r Gvpd_gender, results='asis'}

div(
  class = "dashboard-card", 
 Gvpd_gender$plot,
    tags$span(
      class="sr-only", 
      Gvpd_gender$sr_text)
    )

```


###

```{r Gvpd_race, results='asis'}

div(
  class = "dashboard-card", 
 Gvpd_race$plot,
    tags$span(
      class="sr-only", 
      Gvpd_race$sr_text)
    )

```


### 

```{r Gvpd_eth, results='asis'}

div(
  class = "dashboard-card", 
 Gvpd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Gvpd_ethnicity$sr_text)
    )

```




##

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses</h3>

```{r 04_GVBDs_text, warning=FALSE, results='asis'}

vbds_gwinnett_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_gwinnett_lines, sep = "\n")

cat(" ")

cat("<br>")
```


## VBD Plot

### {.no-title .no-box}

```{r 04_Gwinnett_VBD_barplot, results='asis'}

vbplot_obj <- Gplot_list$bar_chart$`Vectorborne`$plot

vbplot_obj


```


###

```{r Gwinnett_VBD_line, results='asis'}

Gvbplot_list_obj <- Gplot_list$line_charts$`Vectorborne`$plot

Gvbplot_list_obj

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vectorborne Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r results='asis'}

div(
  class = "dashboard-card", 
 Gvbd_gender$plot,
    tags$span(
      class="sr-only", 
      Gvbd_gender$sr_text)
    )

```


### 

```{r results='asis'}

div(
  class = "dashboard-card", 
 Gvbd_race$plot,
    tags$span(
      class="sr-only", 
      Gvbd_race$sr_text)
    )

```


### 

```{r results='asis'}

div(
  class = "dashboard-card", 
 Gvbd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Gvbd_ethnicity$sr_text)
    )


```




## 

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Enteric Illnesses</h3>

```{r 04_Genterics_text, warning=FALSE, results='asis'}
enterics_gwinnett_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_gwinnett_lines, sep = "\n")

cat(" ")

cat("<br>")

```


##

```{r 04_Genterics_plot, warning=FALSE, echo=FALSE, results='asis'}


Geplot_obj <- Gplot_list$bar_chart$`Enteric`$plot

Geplot_obj



```


###

```{r Genterics_time, warning=FALSE, echo=FALSE, results='asis'}

Geplot_list_obj <- Gplot_list$line_charts$`Enteric`$plot

Geplot_list_obj

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Enteric Illnesses</h3>

## {.no-title}

### {.no-title}

```{r Gent_gender, results='asis'}

div(
  class = "dashboard-card", 
 Gent_gender$plot,
    tags$span(
      class="sr-only", 
      Gent_gender$sr_text)
    )

```


### 

```{r Gent_race, results='asis'}
div(
  class = "dashboard-card", 
 Gent_race$plot,
    tags$span(
      class="sr-only", 
      Gent_race$sr_text)
    )
```


### 

```{r Gent_eth, results='asis'}

div(
  class = "dashboard-card", 
 Gent_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Gent_ethnicity$sr_text)
    )
```






# **Newton County**

<h1>Newton County Community Health Data</h1>


```{r Npop_callout, echo=FALSE}
Npop <- "124,010" # Example R calculation
# The 'value' attribute automatically handles the large formatting.
cat(Npop)

valueBox(
  value = Npop,
  icon = "fa-pencil",
  color = "primary"
)
cat(" ")
```


##

### Vaccine Preventables

<h3 style="font-weight=bold; margin:0;">Vaccine Preventable Illnesses in Newton County</h3>

```{r 04_NVPDs_text, results='asis'}
vpds_newton_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vpds_newton_lines, sep = "\n")

cat(" ")

```


###

```{r 04_Newton_VPD_plot, echo=FALSE, warning=FALSE}

plot_obj <- all_plots$Newton$`Vaccine Preventable`$bar

ggplotly(plot_obj$plot)


```


```{r results='asis'}

cat("<br>")

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Hepatitis Illnesses in Newton County</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r nheptime, results='asis'}

div(
  class = "dashboard-card",
  all_hep_plots$Newton$plot,
  tags$span(class = "sr-only", all_hep_plots$Newton$sr_text)
)

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vaccine Preventable Illnesses in Newton County</h3>
  
## {.no-title .no-box}
  
### {.no-title .no-box}

```{r Ngender, results='asis'}


div(
  class = "dashboard-card", 
 Nvpd_gender$plot,
    tags$span(
      class="sr-only", 
      Nvpd_gender$sr_text)
    )


```


###

```{r Nrace, results='asis'}
div(
  class = "dashboard-card", 
 Nvpd_race$plot,
    tags$span(
      class="sr-only", 
      Nvpd_race$sr_text)
    )
```


### 

```{r Neth, results='asis'}

div(
  class = "dashboard-card", 
 Nvpd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Nvpd_ethnicity$sr_text)
    )
```



##

### Vectorborne

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses in Newton County</h3>

```{r 04_NVBDs_text, warning=FALSE, results='asis'}
vbds_newton_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_newton_lines, sep = "\n")
cat(" ")

cat("<br>")

```



## VBD Plot

### {.no-title .no-box}

```{r 04_Newton_VBD_plot, echo=FALSE, results='asis'}

plot_obj <- all_plots$Newton$`Vectorborne`$bar

ggplotly(plot_obj$plot)


```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vectorborne Illnesses in Newton County</h3>
  
## {.no-title .no-box}
  
### {.no-title .no-box}


```{r results='asis'}

div(
  class = "dashboard-card", 
 Nvbd_gender$plot,
    tags$span(
      class="sr-only", 
      Nvbd_gender$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card", 
 Nvbd_race$plot,
    tags$span(
      class="sr-only", 
      Nvbd_race$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card", 
 Nvbd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Nvbd_ethnicity$sr_text)
    )


```




## 

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Enteric Illnesses</h3>

```{r 04_nenterics_text, warning=FALSE, results='asis'}
enterics_newton_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_newton_lines, sep = "\n")
cat(" ")

```


###

```{r 04_Newton_enterics_plot, echo=FALSE, warning=FALSE}


plot_obj <- all_plots$Newton$`Enteric`$bar

ggplotly(plot_obj$plot)

cat(" ")

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Enteric Illnesses</h3>

## {.no-title}

### {.no-title}
  
```{r Ngend, results='asis'}  


div(
  class = "dashboard-card", 
  Nent_gender$plot,
  tags$span(
    class="sr-only", 
    Nent_gender$sr_text)
)

```


### 

```{r Nent_race, results='asis'}
div(
  class = "dashboard-card", 
  Nent_race$plot,
  tags$span(
    class="sr-only", 
    Nent_race$sr_text)
)
```


### 

```{r Nent_eth, results='asis'}

div(
  class = "dashboard-card", 
  Nent_ethnicity$plot,
  tags$span(
    class="sr-only", 
    Nent_ethnicity$sr_text)
)
```


# **Rockdale County** {.tabset}

<h1>Rockdale County Community Health Data</h1>

```{r Rpop_callout, echo=FALSE}
Rpop <- "97,610" # Example R calculation
# The 'value' attribute automatically handles the large formatting.
cat(Rpop)
```


#### Vaccine Preventables

```{r 04_RVPDs_text, warning=FALSE, results='asis'}
vpds_rockdale_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vpds_rockdale_lines, sep = "\n")
cat(" ")


plot_obj <- all_plots$Rockdale$`Vaccine Preventable`$bar
plot_obj$plot
cat("<br><br><br>")
```



### Hepatitis Illnesses in Rockdale County 
-----------------------------------------------------------------------

```{r 04_Rockdale_hep_plot, out.width="100%", echo=FALSE, warning=FALSE, results="asis"}

div(
  class = "dashboard-card",
  all_hep_plots$Rockdale$plot,
  tags$span(class = "sr-only", all_hep_plots$Rockdale$sr_text)
)

cat("<br><br>")
```


### Vaccine Preventable Illnesses 
-----------------------------------------------------------------------

```{r results='asis', out.width="100%", echo=FALSE, warning=FALSE}

plot_obj <- all_plots$Rockdale$`Vaccine Preventable`$trend
plot_obj$plot
cat("<br>")
```



## **Demographic Distribution for Vaccine Preventable Illnesses** 


```{r results='asis'}

cat("<br>")

```


### Gender Distribution
-----------------------------------------------------------------------

```{r results='asis', out.width="80%", echo=FALSE, warning=FALSE}

div(
  class = "dashboard-card", 
 Rvbd_gender$plot,
    tags$span(
      class="sr-only", 
      Rvbd_gender$sr_text)
    )

cat("<br><br><br>")
```


### Race Distribution
-----------------------------------------------------------------------

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Rvbd_race$plot,
    tags$span(
      class="sr-only", 
      Rvbd_race$sr_text)
    )

cat("<br><br><br>")
```


### Ethnicity Distribution
-----------------------------------------------------------------------

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Rvbd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Rvbd_ethnicity$sr_text)
    )

cat("<br><br><br>")
```



```{r results='asis'}

cat("<br><br><br>")

```




##

### Vectorborne

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses in Rockdale County</h3>

```{r 04_RVBDs_text, warning=FALSE, results='asis'}
vbds_rockdale_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_rockdale_lines, sep = "\n")
cat(" ")

cat("<br>")

```




## VBD Plot

### {.no-title .no-box}

```{r 04_Rvbds_text, warning=FALSE, results='asis'}
vbds_rockdale_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_rockdale_lines, sep = "\n")

cat(" ")


plot_obj <- all_plots$Rockdale$`Vectorborne`$bar
plot_obj$plot
cat("<br><br><br>")
```








## **Demographic Distribution for Vectorborne Illnesses**
-----------------------------------------------------------------------

```{r results='asis'}

cat("<br>")

```


### Gender Distribution


```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Rvbd_gender$plot,
    tags$span(
      class="sr-only", 
      Rvbd_gender$sr_text)
    )

cat("<br><br><br>")
```


### Race Distribution


```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Rvbd_race$plot,
    tags$span(
      class="sr-only", 
      Rvbd_race$sr_text)
    )

cat("<br><br><br>")
```


### Ethnicity Distribution


```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Rvbd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Rvbd_ethnicity$sr_text)
    )

cat("<br><br><br>")

```




## Enteric 
------------------------------------------

```{r 04_renterics_text, warning=FALSE, results='asis'}
enterics_rockdale_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_rockdale_lines, sep = "\n")

cat(" ")

```


## **Demographic Distribution for Enteric Illnesses**
----------------------------------------------

```{r results='asis'}

cat("<br>")

```

### Gender Distribution
----------------------------------------------

```{r results='asis', fig.width=6}


div(
  class = "dashboard-card", 
 Rent_gender$plot,
    tags$span(
      class="sr-only", 
      Rent_gender$sr_text)
    )

cat("<br><br><br>")
```

### Race Distribution
---------------------------------------

```{r results='asis', out.width="100%"}
div(
  class = "dashboard-card", 
 Rent_race$plot,
    tags$span(
      class="sr-only", 
      Rent_race$sr_text)
    )
cat("<br><br><br>")
```


### Ethnicity Distribution
------------------------------------------

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Rent_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Rent_ethnicity$sr_text)
    )
cat("<br><br><br>")
```




# **Data Dictionary**
<h1>title</h1>
## {.no-title .no-box}

### {.no-box}

```{r}

cat("*Content coming soon.*")


```





# **About Us**

<h1>title</h1>

## {.no-title .no-box}

### {.no-box}

```{r}

cat("*Content coming soon.*")


```





