---
title: "GNR Public Health's <br>
Notifiable Diseases Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme:
      version: 4 # Explicitly setting the version helps with bslib
      bg: "#FFFFFF"
      fg: "#13293d"
      primary: "#FAA81A"
    includes:
      in_header: OGheader.html
---


```{r setup, include=FALSE, echo=FALSE, warning =FALSE}

knitr::clean_cache(clean = TRUE)
knitr::opts_chunk$set(echo = FALSE)
# opts_chunk$set(comment="")
# 1. Source your theme and your functions (make sure load_plot_object is in here)
source(here("R","brand_theme.R"))
source(here::here("R", "functions.R"))
source(here("R", "plot_accessibility.R"))




## DISTRICT PLOTS
# pre-generated District plots by program
vpds_district_plot <- readRDS(here::here("output", "vpds_district_plot.rds"))
vbds_district_plot <- readRDS(here::here("output", "vbds_district_plot.rds"))
enteric_district_plot <- readRDS(here::here("output", "enterics_district_plot.rds"))


# pre-generated District pies by demographic
vpds_dis_gen_pie <- readRDS(here("output", "vpd_district_gender_pie.rds"))
vpds_dis_rac_pie <- readRDS(here("output", "vpd_district_race_pie.rds"))
vpds_dis_eth_pie <- readRDS(here("output", "vpd_district_ethnicity_pie.rds"))

enterics_dis_gen_pie <- readRDS(here("output", "ent_district_gender_pie.rds"))
enterics_dis_rac_pie <- readRDS(here("output", "ent_district_race_pie.rds"))
enterics_dis_eth_pie <- readRDS(here("output", "ent_district_ethnicity_pie.rds"))

vbds_dis_gen_pie <- readRDS(here("output", "vbd_district_gender_pie.rds"))
vbds_dis_rac_pie <- readRDS(here("output", "vbd_district_race_pie.rds"))
vbds_dis_eth_pie <- readRDS(here("output", "vbd_district_ethnicity_pie.rds"))


## COUNTY PLOTS
# These files will be loaded by the R Markdown dashboard later.
Gvbd_gender <- readRDS(here("output", "Gvbd_gen_pie.rds"))
Gvbd_race <- readRDS(here("output", "Gvbd_rac_pie.rds"))
Gvbd_ethnicity <- readRDS(here("output", "Gvbd_eth_pie.rds"))

Gvpd_gender <- readRDS(here("output", "Gvpd_gen_pie.rds"))
Gvpd_race <- readRDS(here("output", "Gvpd_rac_pie.rds"))
Gvpd_ethnicity <- readRDS(here("output", "Gvpd_eth_pie.rds"))

Gent_gender <- readRDS(here("output", "Gent_gen_pie.rds"))
Gent_race <- readRDS(here("output", "Gent_rac_pie.rds"))
Gent_ethnicity <- readRDS(here("output", "Gent_eth_pie.rds"))

Nvbd_gender <- readRDS(here("output", "Nvbd_gen_pie.rds"))
Nvbd_race <- readRDS(here("output", "Nvbd_rac_pie.rds"))
Nvbd_ethnicity <- readRDS(here("output", "Nvbd_eth_pie.rds"))

Nvpd_gender <- readRDS(here("output", "Nvpd_gen_pie.rds"))
Nvpd_race <- readRDS(here("output", "Nvpd_rac_pie.rds"))
Nvpd_ethnicity <- readRDS(here("output", "Nvpd_eth_pie.rds"))

Nent_gender <- readRDS(here("output", "Nent_gen_pie.rds"))
Nent_race <- readRDS(here("output", "Nent_rac_pie.rds"))
Nent_ethnicity <- readRDS(here("output", "Nent_eth_pie.rds"))


Rvbd_gender <- readRDS(here("output", "Rvbd_gen_pie.rds"))
Rvbd_race <- readRDS(here("output", "Rvbd_rac_pie.rds"))
Rvbd_ethnicity <- readRDS(here("output", "Rvbd_eth_pie.rds"))

Rvpd_gender <- readRDS(here("output", "Rvpd_gen_pie.rds"))
Rvpd_race <- readRDS(here("output", "Rvpd_rac_pie.rds"))
Rvpd_ethnicity <- readRDS(here("output", "Rvpd_eth_pie.rds"))

Rent_gender <- readRDS(here("output", "Rent_gen_pie.rds"))
Rent_race <- readRDS(here("output", "Rent_rac_pie.rds"))
Rent_ethnicity <- readRDS(here("output", "Rent_eth_pie.rds"))


# Hepatitis Data
# district_hep_object <- readRDS(here("output", "district_hep_time.rds"))
# Gwinnett_hep_object <- readRDS(here("output", "Gwinnett_hep_time.rds"))
# Newton_hep_object <- readRDS(here("output", "Newton_hep_time.rds"))
# Rockdale_hep_object <- readRDS(here("output", "Rockdale_hep_time.rds"))


# --- Define counties and programs ---
county_name <- c("Gwinnett", "Newton", "Rockdale")
program_name <- c("Vaccine Preventable", "Vectorborne", "Enteric")

# VPD_program_name <- program_name[1] # "Vaccine Preventable"
# VBD_program_name <- program_name[2] # "Vectorborne"
# ENTERIC_program_name <- program_name[3] # "Enteric"

hepatits <- readRDS(here("hepatitis.rds"))

# 2. Keep only the "Global" objects you need for things like narratives
# Narrative file mapping
narrative_files <- list(
  "Vaccine Preventable" = "VPDs.Rmd",
  "Vectorborne" = "VBDs.Rmd",
  "Enteric" = "Enterics.Rmd",
  "Hep_C" = "Hepatitis_C.Rmd",
  "about_lines" = "about_dashboard.Rmd")


# Load all plots
all_plots <- readRDS(here::here("output", "plots", "all_dashboard_plots.rds"))
# all_hep_plots <- readRDS(here::here("output", "plots", "all_hep_plots.rds"))
Gplot_list <- readRDS(here("output", "plots", "gwinnett_linebar_plots.rds"))

# 3. Define shorthand tags
tags <- htmltools::tags
div <- htmltools::div
```

<!-- # For skip link #main ID -->
<div id="main" tabindex="-1" style="outline: none;"></div>

# **Notifiable Diseases Dashboard Overview** {.sidebar data-width=150}

##### Accessibility Settings

<div class="accessibility-controls">
  <button id="contrast-toggle" class="btn-accessibility">
    <i class="fa fa-adjust"></i> HIGH CONTRAST MODE
  </button>
</div>


####

```{r About_summary, warning=FALSE, results='asis'}

# Read the pre-generated text summary
about_lines <- readLines(here("narratives","about_dashboard.Rmd"))

# 2. Print the lines using cat() with a newline separator, cat() is used because it prints text directly, honoring the Markdown formatting.
 cat(about_lines, sep = "\n")
 cat(" ")

```



```{r logo, results='asis'}

htmltools::includeHTML("header.html")


# This reads the content of header.html and injects it directly into the RMD document
cat(readLines("OGheader.html"), sep = "\n")

logo <- here("GNR_logo.png")
tags$img(
  src = logo,
  alt="GNR Public Health Department Logo", style="max-width: 100%; height: auto;")

```

<p><strong>Last Updated:</strong> <script>document.write(new Date().toLocaleDateString());</script></p>

# **About Us**

```{r aboutus_text, warning=FALSE, results='asis'}
# Read the pre-generated text summary
about_lines <- readLines(here("narratives","aboutus.Rmd"))

# 2. Print the lines using cat() with a newline separator, cat() is used because it prints text directly, honoring the Markdown formatting.
 cat(about_lines, sep = "\n")
 cat(" ")

```




# Vaccine-Preventable Illnesses {data-navmenu="District Overview"}

```{r VPDs_summary, warning=FALSE, results='asis'}

# Read the pre-generated text summary
vpds_district_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator, cat() is used because it prints text directly, honoring the Markdown formatting.
 cat(vpds_district_lines, sep = "\n")
 cat(" ")

```



```{r 04_VPDs_district_plot, results='asis'}

div(
  class = "dashboard-card",
 vpds_district_plot$plot,
    tags$span(
      class="sr-only",
      vpds_district_plot$sr_text)
    )

cat(" ")

```

```{r results='asis'}

cat("<br>")

```

##  {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vaccine Preventable Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r district_gender, results='asis'}

 div(
  class = "dashboard-card",
 vpds_dis_gen_pie$plot,
    tags$span(
      class="sr-only",
      vpds_dis_gen_pie$sr_text)
    )

```


###

```{r district_ethnicity, results='asis'}

div(
  class = "dashboard-card",
 vpds_dis_eth_pie$plot,
    tags$span(
      class="sr-only",
      vpds_dis_eth_pie$sr_text)
    )

```


###

```{r district_race, results='asis'}

div(
  class = "dashboard-card",
 vpds_dis_rac_pie$plot,
    tags$span(
      class="sr-only",
      vpds_dis_rac_pie$sr_text)
    )


```


##

```{r, results='asis'}

cat("<br>")

```


## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Hepatitis Illnesses across the District</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r Hepatitis_C, warning=FALSE, results='asis'}

# Read the pre-generated  text summary
hepc_district_lines <- readLines(here("narratives", "Hepatitis_C.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(hepc_district_lines, sep = "\n")

cat(" ")

```



<!-- ```{r hep_plot, results='asis'} -->


<!-- div( -->
<!--   class = "dashboard-card",  -->
<!--  district_hep_object$plot, -->
<!--     tags$span( -->
<!--       class="sr-only",  -->
<!--       district_hep_object$sr_text) -->
<!--     ) -->

<!-- cat("<br>") -->

<!-- ``` -->





# Enteric Illnesses {data-navmenu="District Overview"}

```{r 04_Enterics_Summary, results='asis'}
# Read the pre-generated accessible text summary
enterics_district_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_district_lines, sep = "\n")


cat(" ")
```



```{r 04_Enterics_district_plot, warning=FALSE, results='asis'}

div(
  class = "dashboard-card",  # <- apply the global card style
enteric_district_plot$plot,
     tags$span(
       class="sr-only",
       enteric_district_plot$sr_text)
)
cat("<br>")

```




## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Enteric Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r ent_dis_gen, results='asis'}


div(
  class = "dashboard-card",
 enterics_dis_gen_pie$plot,
    tags$span(
      class="sr-only",
      enterics_dis_gen_pie$sr_text)
    )

```


###

```{r ent_dis_race, results='asis'}

div(
  class = "dashboard-card",
 enterics_dis_rac_pie$plot,
    tags$span(
      class="sr-only",
      enterics_dis_rac_pie$sr_text)
    )

```


###

```{r ent_dis_ethnicity, results='asis'}

div(
  class = "dashboard-card",
 enterics_dis_eth_pie$plot,
    tags$span(
      class="sr-only",
      enterics_dis_eth_pie$sr_text)
    )

```





# Vectorborne Illnesses {data-navmenu="District Overview"}

```{r 04_VBD_text, warning=FALSE, results='asis'}

# Read the pre-generated accessible text summary
vbds_district_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_district_lines, sep = "\n")


cat(" ")

```


```{r 04_VBDs_district_plot, warning=FALSE, results='asis'}

div(
  class = "dashboard-card",  # <- apply the global card style
vbds_district_plot$plot,
     tags$span(
       class="sr-only",
       vbds_district_plot$sr_text)
)
cat(" ")

```





## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vectorborne Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r vbd_dis_gen, results='asis'}


div(
  class = "dashboard-card",
 vbds_dis_gen_pie$plot,
    tags$span(
      class="sr-only",
      vbds_dis_gen_pie$sr_text)
    )

```



###

```{r vbd_dis_race, results='asis'}


div(
  class = "dashboard-card",
 vbds_dis_rac_pie$plot,
    tags$span(
      class="sr-only",
      vbds_dis_rac_pie$sr_text)
    )

```



###

```{r vbd_dis_ethnicity, results='asis'}


div(
  class = "dashboard-card",
 vbds_dis_eth_pie$plot,
    tags$span(
      class="sr-only",
      vbds_dis_eth_pie$sr_text)
    )

```





# **Gwinnett County**


## Population {.no-title .no-box}

### 📈 Gwinnett Population: {.no-box data-width=150}

```{r Gpop_callout, echo=FALSE}


Gpop <- "1,003,869" # Example R calculation
# The 'value' attribute automatically handles the large formatting.


valueBox(
  value = Gpop,
  icon = "fa-pencil",
  color = "primary"
)
cat(" ")


```




##

###

<h3 style="font-weight=bold; margin:0;">Vaccine Preventable Illnesses</h3>


```{r 04_GVPDs_text, results='asis'}

vpds_gwinnett_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vpds_gwinnett_lines, sep = "\n")

cat(" ")

cat("<br>")

```


##

```{r GVPD_bar, results='asis'}

vplot_obj <- Gplot_list$bar_chart$`Vaccine Preventable`$plot

vplot_obj


```

###

```{r GVPD_timeplot, results='asis'}


Gvplot_list_obj <- Gplot_list$line_charts$`Vaccine Preventable`$plot

Gvplot_list_obj


```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vaccine Preventable Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r Gvpd_gender, results='asis'}

div(
  class = "dashboard-card",
 Gvpd_gender$plot,
    tags$span(
      class="sr-only",
      Gvpd_gender$sr_text)
    )

```


###

```{r Gvpd_race, results='asis'}

div(
  class = "dashboard-card",
 Gvpd_race$plot,
    tags$span(
      class="sr-only",
      Gvpd_race$sr_text)
    )

```


###

```{r Gvpd_eth, results='asis'}

div(
  class = "dashboard-card",
 Gvpd_ethnicity$plot,
    tags$span(
      class="sr-only",
      Gvpd_ethnicity$sr_text)
    )

```




##

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses</h3>

```{r 04_GVBDs_text, warning=FALSE, results='asis'}

vbds_gwinnett_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_gwinnett_lines, sep = "\n")

cat(" ")

cat("<br>")
```


## VBD Plot

### {.no-title .no-box}

```{r 04_Gwinnett_VBD_barplot, results='asis'}

vbplot_obj <- Gplot_list$bar_chart$`Vectorborne`$plot

vbplot_obj


```


###

```{r Gwinnett_VBD_line, results='asis'}

Gvbplot_list_obj <- Gplot_list$line_charts$`Vectorborne`$plot

Gvbplot_list_obj

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vectorborne Illnesses</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r results='asis'}

div(
  class = "dashboard-card",
 Gvbd_gender$plot,
    tags$span(
      class="sr-only",
      Gvbd_gender$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Gvbd_race$plot,
    tags$span(
      class="sr-only",
      Gvbd_race$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Gvbd_ethnicity$plot,
    tags$span(
      class="sr-only",
      Gvbd_ethnicity$sr_text)
    )


```




##

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Enteric Illnesses</h3>

```{r 04_Genterics_text, warning=FALSE, results='asis'}
enterics_gwinnett_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_gwinnett_lines, sep = "\n")

cat(" ")

cat("<br>")

```


##

```{r 04_Genterics_plot, warning=FALSE, echo=FALSE, results='asis'}


Geplot_obj <- Gplot_list$bar_chart$`Enteric`$plot

Geplot_obj



```


###

```{r Genterics_time, warning=FALSE, echo=FALSE, results='asis'}

Geplot_list_obj <- Gplot_list$line_charts$`Enteric`$plot

Geplot_list_obj

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Enteric Illnesses</h3>

## {.no-title}

### {.no-title}

```{r Gent_gender, results='asis'}

div(
  class = "dashboard-card",
 Gent_gender$plot,
    tags$span(
      class="sr-only",
      Gent_gender$sr_text)
    )

```


###

```{r Gent_race, results='asis'}
div(
  class = "dashboard-card",
 Gent_race$plot,
    tags$span(
      class="sr-only",
      Gent_race$sr_text)
    )
```


###

```{r Gent_eth, results='asis'}

div(
  class = "dashboard-card",
 Gent_ethnicity$plot,
    tags$span(
      class="sr-only",
      Gent_ethnicity$sr_text)
    )
```






# **Newton County**

## Population {.no-title .no-box}

### 📈 Newton Population

```{r Npop_callout, echo=FALSE}
Npop <- "124,010" # Example R calculation
# The 'value' attribute automatically handles the large formatting.
cat(Npop)

valueBox(
  value = Npop,
  icon = "fa-pencil",
  color = "primary"
)
cat(" ")
```


##

### Vaccine Preventables

<h3 style="font-weight=bold; margin:0;">Vaccine Preventable Illnesses in Newton County</h3>

```{r 04_NVPDs_text, results='asis'}
vpds_newton_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vpds_newton_lines, sep = "\n")

cat(" ")

```


###

```{r 04_Newton_VPD_plot, echo=FALSE, warning=FALSE, results='asis'}

plot_obj <- all_plots$Newton$`Vaccine Preventable`$bar

ggplotly(plot_obj$plot)


```


```{r results='asis'}

cat("<br>")

```



<!-- ## {data-height=40} -->

<!-- ### {.no-title .no-box} -->

<!-- <h3 style="font-weight=bold; margin:0;">Hepatitis Illnesses in Newton County</h3> -->

<!-- ## {.no-title .no-box} -->

<!-- ### {.no-title .no-box} -->

<!-- ```{r nheptime, results='asis'} -->

<!-- # 1. Grab the object from the master list -->
<!-- plot_obj <- all_hep_plots$Newton_Hep_time -->

<!-- # 2. Wrap it in the dashboard-card div -->
<!-- htmltools::tagList( -->
<!--   htmltools::tags$div( -->
<!--     class = "dashboard-card",  -->
<!--     plot_obj$plot, -->
<!--     htmltools::tags$span( -->
<!--       class = "sr-only",  -->
<!--       plot_obj$sr_text -->
<!--     ) -->
<!--   ) -->
<!-- ) -->



<!-- ``` -->



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vaccine Preventable Illnesses in Newton County</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r Ngender, results='asis'}


div(
  class = "dashboard-card",
 Nvpd_gender$plot,
    tags$span(
      class="sr-only",
      Nvpd_gender$sr_text)
    )


```


###

```{r Nrace, results='asis'}
div(
  class = "dashboard-card",
 Nvpd_race$plot,
    tags$span(
      class="sr-only",
      Nvpd_race$sr_text)
    )
```


###

```{r Neth, results='asis'}

div(
  class = "dashboard-card",
 Nvpd_ethnicity$plot,
    tags$span(
      class="sr-only",
      Nvpd_ethnicity$sr_text)
    )
```



##

### Vectorborne

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses in Newton County</h3>

```{r 04_NVBDs_text, warning=FALSE, results='asis'}
vbds_newton_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_newton_lines, sep = "\n")
cat(" ")

cat("<br>")

```



## VBD Plot

### {.no-title .no-box}

```{r 04_Newton_VBD_plot, echo=FALSE, results='asis'}

plot_obj <- all_plots$Newton$`Vectorborne`$bar

plot_obj$plot


```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vectorborne Illnesses in Newton County</h3>

## {.no-title .no-box}

### {.no-title .no-box}


```{r results='asis'}

div(
  class = "dashboard-card",
 Nvbd_gender$plot,
    tags$span(
      class="sr-only",
      Nvbd_gender$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Nvbd_race$plot,
    tags$span(
      class="sr-only",
      Nvbd_race$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Nvbd_ethnicity$plot,
    tags$span(
      class="sr-only",
      Nvbd_ethnicity$sr_text)
    )


```




##

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Enteric Illnesses</h3>

```{r 04_nenterics_text, warning=FALSE, results='asis'}
enterics_newton_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_newton_lines, sep = "\n")
cat(" ")

```


### Enteric Plot

```{r 04_Newton_enterics_plot, echo=FALSE, warning=FALSE, results='asis'}


plot_obj <- all_plots$Newton$`Enteric`$bar

ggplotly(plot_obj$plot)

cat(" ")

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Enteric Illnesses in Newton County</h3>

## {.no-title}

### {.no-title}

```{r Ngend, results='asis'}


div(
  class = "dashboard-card",
  Nent_gender$plot,
  tags$span(
    class="sr-only",
    Nent_gender$sr_text)
)

```


###

```{r Nent_race, results='asis'}
div(
  class = "dashboard-card",
  Nent_race$plot,
  tags$span(
    class="sr-only",
    Nent_race$sr_text)
)
```


###

```{r Nent_eth, results='asis'}

div(
  class = "dashboard-card",
  Nent_ethnicity$plot,
  tags$span(
    class="sr-only",
    Nent_ethnicity$sr_text)
)
```





# **Rockdale County** {.tabset}

### 📈 Rockdale Population: 97,610 {.no-title .no-box}

```{r Rpop_callout, echo=FALSE}
Rpop <- "97,610" # Example R calculation
# The 'value' attribute automatically handles the large formatting.
cat(Rpop)
```


##

###

<h3 style="font-weight=bold; margin:0;">Vaccine Preventable Illnesses in Rockdale County</h3>

```{r 04_RVPDs_text, warning=FALSE, results='asis'}

vpds_rockdale_lines <- readLines(here("narratives","VPDs.Rmd"))


cat(vpds_rockdale_lines, sep = "\n")
cat(" ")



cat("<br>")
```


```{r RVPD_bar, results='asis'}

plot_obj <- all_plots$Rockdale$`Vaccine Preventable`$bar
plot_obj$plot

```


```{r RVPD_timeplot, results='asis'}

plot_obj <- all_plots$Rockdale$`Vaccine Preventable`$trend
plot_obj$plot
```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vaccine Preventable Illnesses in Rockdale County</h3>

## {.no-title .no-box}

### {.no-title .no-box}


```{r Rvpd_gender, results='asis'}

div(
  class = "dashboard-card",
 Rvpd_gender$plot,
    tags$span(
      class="sr-only",
      Rvpd_gender$sr_text)
    )

```


###

```{r Rvpd_race, results='asis'}

div(
  class = "dashboard-card",
 Rvpd_race$plot,
    tags$span(
      class="sr-only",
      Rvpd_race$sr_text)
    )

```


###

```{r Rvpd_eth, results='asis'}

div(
  class = "dashboard-card",
 Rvpd_ethnicity$plot,
    tags$span(
      class="sr-only",
      Rvpd_ethnicity$sr_text)
    )

```




##

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses in Rockdale County</h3>

```{r 04_Rvbds_text, warning=FALSE, results='asis'}
vbds_rockdale_lines <- readLines(here("narratives","VBDs.Rmd"))

cat(vbds_rockdale_lines, sep = "\n")

cat(" ")
```


## VBD Plot

### {.no-title .no-box}

```{r 04_RVBD_barplot, results='asis'}

plot_obj <- all_plots$Rockdale$`Vectorborne`$bar
plot_obj$plot
```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Vectorborne Illnesses in Rockdale County</h3>

## {.no-title .no-box}

### {.no-title .no-box}

```{r results='asis'}

div(
  class = "dashboard-card",
 Rvbd_gender$plot,
    tags$span(
      class="sr-only",
      Rvbd_gender$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Rvbd_race$plot,
    tags$span(
      class="sr-only",
      Rvbd_race$sr_text)
    )

```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Rvbd_ethnicity$plot,
    tags$span(
      class="sr-only",
      Rvbd_ethnicity$sr_text)
    )


```




##

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Enteric Illnesses</h3>

```{r 04_renterics_text, warning=FALSE, results='asis'}
enterics_rockdale_lines <- readLines(here("narratives","Enterics.Rmd"))

cat(enterics_rockdale_lines, sep = "\n")

cat(" ")

```


##

```{r 04_Renterics_plot, results='asis'}


# Replot_obj <- Rplot_list$bar_chart$`Enteric`$plot
#
# Replot_obj



```


###

```{r renterics_time, results='asis'}

# Replot_list_obj <- Rplot_list$line_charts$`Enteric`$plot
#
# Replot_list_obj

```



## {data-height=40}

### {.no-title .no-box}

<h3 style="font-weight=bold; margin:0;">Demographic Distribution for Enteric Illnesses in Rockdale County</h3>

## {.no-title}

### {.no-title}


```{r results='asis'}


div(
  class = "dashboard-card",
 Rent_gender$plot,
    tags$span(
      class="sr-only",
      Rent_gender$sr_text)
    )

```


###

```{r results='asis'}
div(
  class = "dashboard-card",
 Rent_race$plot,
    tags$span(
      class="sr-only",
      Rent_race$sr_text)
    )
```


###

```{r results='asis'}

div(
  class = "dashboard-card",
 Rent_ethnicity$plot,
    tags$span(
      class="sr-only",
      Rent_ethnicity$sr_text)
    )
```





# **Data Dictionary**

```{r, dd}
# # Read the pre-generated text summary
# ddictionary <- readLines(here("narratives","ddictionary.Rmd"))
#
# # 2. Print the lines using cat() with a newline separator, cat() is used because it prints text directly, honoring the Markdown formatting.
#  cat(ddictionary, sep = "\n")
#  cat(" ")
```








# **Community Health**

<h3 style="font-weight=bold; margin:0;">Vectorborne Illnesses in Newton County</h3>





```{r ch, warning=FALSE, results='asis'}
vbds_newton_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_newton_lines, sep = "\n")
cat(" ")

cat("<br>")

```



## VBD Plot

### {.no-title .no-box}

```{r testNewton_VBD_plot, echo=FALSE, results='asis'}

plot_obj <- all_plots$Newton$`Vectorborne`$bar

plot_obj$plot


```


# Hepatitis TIme Series Plot

### {.no-title .no-box}

```{r testhep_VBD_plot, echo=FALSE, results='asis'}

hepatits

hepatits$plot


```


## VBD Plot

### {.no-title .no-box}

```{r test_VBD_plot, echo=FALSE, results='asis'}

plot_obj <- all_plots$Newton$`Vectorborne`$bar

plot_obj$plot


```
