---
title: "GNR Public Health's <br>
Notifiable Diseases Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    theme:
      version: 4 # Explicitly setting the version helps with bslib
      bg: "#FFFFFF"
      fg: "#13293d" 
      primary: "#FAA81A"
    includes:
      in_header: OGheader.html
runtime: shiny # Essential for interactivity with Shiny inputs/outputs
---

```{r setup, include=FALSE, echo=FALSE, warning =FALSE}

knitr::clean_cache(clean = TRUE)
knitr::opts_chunk$set(echo = FALSE)
# opts_chunk$set(comment="")
# 1. Source your theme and your functions (make sure load_plot_object is in here)
library(here)

source("R/packages.R")
source(here("R","brand_theme.R"))
source(here::here("R", "functions.R"))

# 2. Data Ingestion ----
# Loads raw data from a file into R's memory.
print("Step 1: Loading raw data...")
source("R/01_data_import.R")


# 3. Data Wrangling and Transformation ----
# Cleans and transforms the data for data analysis
# These scripts create cleaned dataframes and save them as .rds and .csv files.
print("Step 2: Cleaning and transforming data...")
source("R/02_enteric_script.R")
source("R/02_vax_script.R")
source("R/02_VBD_script.R")


# 4. Exploratory Data Analysis (EDA) and Visualization ----
# Generates plots and summary tables for EDA.
print("Step 3: Creating exploratory plots...")
source("R/03_combined_data.R")
source("R/05a_generate_county_plots.R")
source("R/05b_county_plots_readin.R")
source("R/05_Gwinnett_county_plot.R")
source("R/Gwinnett_pie_demo.R")
source("R/hep_timeseries.R")
source("R/5_year_county.R")


# --- Define counties and programs ---
county_name <- c("Gwinnett", "Newton", "Rockdale")
program_name <- c("Vaccine Preventable", "Vectorborne", "Enteric")

VPD_program_name <- program_name[1] # "Vaccine Preventable"
VBD_program_name <- program_name[2] # "Vectorborne"
ENTERIC_program_name <- program_name[3] # "Enteric"

# Pre-generated plot file mapping
plot_files <- list(
  "Vaccine Preventable" = "vpds_plot.rds",
  "Vectorborne" = "vbds_plot.rds",
  "Enteric" = "enterics_plot.rds"
)

# 2. Keep only the "Global" objects you need for things like narratives
# Narrative file mapping
narrative_files <- list(
  "Vaccine Preventable" = "VPDs.Rmd",
  "Vectorborne" = "VBDs.Rmd",
  "Enteric" = "Enterics.Rmd",
  "Hep_C" = "Hepatitis_C.rmd",
  "about_lines" = "about_dashboard.rmd")


# Load all plots
plot_object <- readRDS(here::here("output", "all_dashboard_plots.rds"))


# 3. Define shorthand tags
tags <- htmltools::tags
div <- htmltools::div
```


# **Gwinnett County** {.tabset}

### Vaccine Preventable {.rows data-navmenu="Gwinnett County"}


📈 Gwinnett Population: 
```{r Gpop_callout, echo=FALSE}


Gpop <- "1,003,869" # Example R calculation
# The 'value' attribute automatically handles the large formatting.


valueBox(
  value = Gpop,
  icon = "fa-pencil",
  color = "primary"
)

```



```{r 04_GVPDs_text, warning=FALSE, results='asis'}
vpds_gwinnett_lines <- readLines(here("narratives","VPDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vpds_gwinnett_lines, sep = "\n")

cat(" ")


```


#### Vaccine Preventable Plot

```{r 04_Gwinnett_VPD_plot, echo=FALSE, warning=FALSE}
# 
# 
# # Fetch it
# vpd_data <- load_plot_object("Gwinnett", "Vaccine Preventable", "bar")
# 
# # Show it
# if(!is.null(vpd_data)){# We use tagList to wrap multiple HTML elements together
#   # We use print() because results='asis' requires explicit output
#     tags$div(
#       class = "dashboard-card",
#       vpd_data$plot,
#       tags$span(
#         class = "sr-only", 
#         vpd_data$sr_text
#    ))
# } else {
#   # Fallback message if file is missing
#   cat("<p>Data not available for this section.</p>")
# }

```


```{r 04_Gwinnett_VPD_bar5, echo=FALSE, warning=FALSE}


# To get the 5-year Bar Chart
vpd_bar_bundle <- load_plot_object("Gwinnett", "Vaccine Preventable", "percent")
vpd_bar_bundle$plot

# Show it
if(!is.null(vpd_data5)){# We use tagList to wrap multiple HTML elements together
  # We use print() because results='asis' requires explicit output
    tags$div(
      class = "dashboard-card",
vpd_bar_bundle$plot,
      tags$span(
        class = "sr-only", 
        vpd_bar_bundle$sr_text
   ))
} else {
  # Fallback message if file is missing
  cat("<p>Data not available for this section.</p>")
}


```


```{r 04_Gwinnett_VPD_trend5, echo=FALSE, warning=FALSE}

# To get the 5-year Rate Trend
vpd_trend_bundle <- load_plot_object("Gwinnett", "Vaccine Preventable", "trend")
vpd_trend_bundle$plot

# Show it
if(!is.null(vpd_data5)){# We use tagList to wrap multiple HTML elements together
  # We use print() because results='asis' requires explicit output
    tags$div(
      class = "dashboard-card",
      vpd_trend_bundle$plot,
      tags$span(
        class = "sr-only", 
        vpd_trend_bundle$sr_text
   ))
} else {
  # Fallback message if file is missing
  cat("<p>Data not available for this section.</p>")
}

```




#### Hepatitis Illnesses in Gwinnett County

```{r results='asis', out.width="100%"}


div(
  class = "dashboard-card", 
 Gwinnett_hep_object$plot,
    tags$span(
      class="sr-only", 
      Gwinnett_hep_object$sr_text)
    )

cat("<br><br><br>")
```


#### **Demographic Distribution for Vaccine Preventable Illnesses**


```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gvpd_gender$plot,
    tags$span(
      class="sr-only", 
      Gvpd_gender$sr_text)
    )

cat("<br><br><br>")
```



```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gvpd_race$plot,
    tags$span(
      class="sr-only", 
      Gvpd_race$sr_text)
    )

cat("<br><br><br>")
```



```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gvpd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Gvpd_ethnicity$sr_text)
    )

cat("<br><br><br>")
```



```{r results='asis', out.width="100%"}
 

div(
  class = "dashboard-card", 
 Gvpd_case_def$plot,
    tags$span(
      class="sr-only", 
      Gvpd_case_def$sr_text)
    )

cat("<br><br><br>")

```




### Vectorborne {data-navmenu="Gwinnett County"}

```{r 04_GVBDs_text, warning=FALSE, results='asis'}
vbds_gwinnett_lines <- readLines(here("narratives","VBDs.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(vbds_gwinnett_lines, sep = "\n")

cat(" ")

```


#### Vectorborne Plot

```{r 04_Gwinnett_VBD_plot, echo=FALSE, warning=FALSE}

# Fetch it
vbd_data <- load_plot_object("Gwinnett", "Vectorborne", "bar")

# Show it
if(!is.null(vbd_data)){# We use tagList to wrap multiple HTML elements together
  # We use print() because results='asis' requires explicit output
    tags$div(
      class = "dashboard-card",
      vbd_data$plot,
      tags$span(
        class = "sr-only", 
        vbd_data$sr_text
   ))
} else {
  # Fallback message if file is missing
  cat("<p>Data not available for this section.</p>")
}

cat("<br><br><br>")
```




### **Demographic Distribution for Vectorborne Illnesses**

#### Gender Distribution

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gvbd_gender$plot,
    tags$span(
      class="sr-only", 
      Gvbd_gender$sr_text)
    )

cat("<br><br><br>")
```


### Race Distribution

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gvbd_race$plot,
    tags$span(
      class="sr-only", 
      Gvbd_race$sr_text)
    )

cat("<br><br><br>")
```


#### Ethnicity Distribution

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gvbd_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Gvbd_ethnicity$sr_text)
    )

cat("<br><br><br>")

```


### Case Definition

```{r results='asis', out.width="100%"}


div(
  class = "dashboard-card", 
 Gvbd_case_def$plot,
    tags$span(
      class="sr-only", 
      Gvbd_case_def$sr_text)
    )

cat("<br><br><br>")
```



### Enteric {data-navmenu="Gwinnett County"}

```{r 04_Genterics_text, warning=FALSE, results='asis'}
enterics_gwinnett_lines <- readLines(here("narratives","Enterics.Rmd"))

# 2. Print the lines using cat() with a newline separator
#    cat() is used because it prints text directly, honoring the Markdown formatting.
cat(enterics_gwinnett_lines, sep = "\n")

cat(" ")

```



```{r 04_Genterics_plot, warning=FALSE, echo=FALSE}

# Fetch it
enteric_data <- load_plot_object("Gwinnett", "Enteric", "bar")

# Show it
if(!is.null(enteric_data)){# We use tagList to wrap multiple HTML elements together
  # We use print() because results='asis' requires explicit output
    tags$div(
      class = "dashboard-card",
      enteric_data$plot,
      tags$span(
        class = "sr-only", 
        enteric_data$sr_text
   ))
} else {
  # Fallback message if file is missing
  cat("<p>Data not available for this section.</p>")
}

cat("<br><br><br>")

```





#### **Demographic Distribution for Enteric Illnesses**

#### Gender Distribution

```{r results='asis', out.width="100%"}


div(
  class = "dashboard-card", 
 Gent_gender$plot,
    tags$span(
      class="sr-only", 
      Gent_gender$sr_text)
    )

cat("<br><br><br>")
```

### Race Distribution

```{r results='asis', out.width="100%"}
div(
  class = "dashboard-card", 
 Gent_race$plot,
    tags$span(
      class="sr-only", 
      Gent_race$sr_text)
    )
cat("<br><br><br>")
```


#### Ethnicity Distribution

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gent_ethnicity$plot,
    tags$span(
      class="sr-only", 
      Gent_ethnicity$sr_text)
    )
cat("<br><br><br>")
```



### Case Definition

```{r results='asis', out.width="100%"}

div(
  class = "dashboard-card", 
 Gent_case_def$plot,
    tags$span(
      class="sr-only", 
      Gent_case_def$sr_text)
    )
```

## 

```{r results='asis', out.width="100%"}
cat("<br><br><br>")

```

